External Patch Group Prior Guided Internal Prior Learning for Real Image Denoising

### 2016-10-27 CVPR2017_Review_Unified.tex
add

The rest of this paper will be summerized as follows: in Section 2, we briefly introduce the related work; in Section 3, we develop the proposed external prior guided internal prior learning model; in Section 4, we formulate the overall image denoising algorithm; in Section 4, we demonstrate extensive experiments on real image denoising probelm; in Section 5, we conclude our paper and give future work.

\section{Related Work}
\subsection{Patch Group Prior of Natural Images}

@@

\section{External Patch Group Prior Guided Internal Prior Learning}

In this section, we formulate the framework of external patch group (PG) prior guided internal orthogonal dictionary learning. We first introduce the patch PG leaning on clean natural RGB images. Then we propose to exploy the external PG prior to guide the internal clustering and orthogonal dictionary learning (DL). The orthogonal DL has alternative closed-form solutions in term of updating sparse coefficients and dictionary. Finally, we discuss the advantages of our proposed external PG prior guided internal orthogonal dictionary learning algorithm.

@@

Now, we have clustered the PGs extracted from external clean images into $K$ Gaussians or subspaces. To better characterize each subspace, we perform singular value decomposition (SVD) on the covariance matrix:
\vspace{-2mm}
\begin{equation}\label{equ3}\vspace{-2mm}
\mathbf{\Sigma}_{k}=\mathbf{U}_{k}\mathbf{S}_{k}\mathbf{U}_{k}^{T}.
\end{equation}
The singular vector matrices $\{\mathbf{U}_{k}\}_{k=1}^{K}$ are employed as the external orthogonal dictionary to guide the internal dictionary learning. The singular values in the diagonal of $\mathbf{S}_{k}$ reflect the significance of the singular vectors in $\mathbf{U}_{k}$ and utilized as prior weights for weighted sparse coding which will be discussed in next section.

@@

Given a real noisy image, we extract the noisy PGs and corresponding mean vectors. Each mean substracted PG is defined as $\mathbf{\overline{Y}}\triangleq \{\mathbf{\overline{x}}_{m}\}_{m=1}^{M}$. Noted that, different from the external PGs, the mean vectors of the internal noisy PGs are saved for recovering. For adaptivity, we project the PG $\mathbf{\overline{Y}}$ into its most suitable Gaussian component (subspace) of the GMM learned on external PGs. The subspace most suitable for $\mathbf{\overline{Y}}$ is selected by firstly calculating the posterior probability of "$\mathbf{\overline{Y}}$ belonging to the $k$th Gaussian component":
\vspace{-2mm}
\begin{equation}\label{equ4}\vspace{-1mm}
P(k|\mathbf{\overline{Y}})=\frac{\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{y}}_{m}|\mathbf{0},\mathbf{\Sigma}_{k})}{\sum_{l=1}^{K}\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{y}}_{m}|\mathbf{0},\mathbf{\Sigma}_{l})},
\end{equation}
and then choosing the component with the maximum A-posteriori (MAP) probability $\ln P(k|\mathbf{\overline{Y}})$.

@@

Assume we have assigned all internal noisy PGs to their corresponding most suitable Gaussians or subspaces in $\{\mathcal{N}(\mathbf{0},\mathbf{\Sigma}_{k})\}_{k=1}^{K}$. For noisy PGs $\mathbf{Y}=[\mathbf{y}_{1},...,\mathbf{y}_{N_{k}}]$ in the $k$-th subspace, we consider to utilize the external orthogonal dictionary to guide the learning of an orthogonal dictionary $\mathbf{D}_{k}:=[\mathbf{D}_{k,e}\ \mathbf{D}_{k,i}]\in \mathbb{R}^{3p^2\times 3p^2}$. This dictionary has two parts: the external part $\mathbf{D}_{k,e}=\mathbf{U}_{k}(:,1:3p^2-r)\in\mathbb{R}^{3p^2\times (3p^2-r)}$ is obtained from the external prior by Equ. (\ref{equ3}), and the internal part $\mathbf{D}_{k,i}$ is consisted of adaptive dictionary atoms learned from the internal noisy PGs. The learning and denoising are simultaneously performed under the proposed reweighted sparse coding framework as f(for notation simplicity, we ignore the subspace index $k$):
\vspace{-2mm}
\begin{equation}\label{equ5}\vspace{-2mm}
\begin{split}
&\min_{\mathbf{D}_{i},\{\bm{\alpha}_{n}\}}
\sum_{n=1}^{N}(\|\mathbf{y}_{n}-\mathbf{D}\bm{\alpha}_{n}\|_{2}^{2}+\sum_{j=1}^{3p^{2}}\lambda_{j}|\bm{\alpha}_{n,j}|)
\\
&
\text{s.t.}
\quad
\mathbf{D}=[\mathbf{D}_{e}\ \mathbf{D}_{i}],\ \mathbf{D}_{i}^{T}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{T}\mathbf{D}_{i} = \mathbf{0},
\end{split}
\end{equation}
where $\lambda_{j}$ is the $j$-th regularization parameter defined as
\vspace{-2mm}
\begin{equation}\label{equ6}\vspace{-2mm}
\lambda_{j} = \lambda/(\sqrt{\mathbf{S}_{j}}+\varepsilon).
\end{equation}
We employ square roots of the singular values in $\mathbf{S}$ (please refer Equ. (\ref{equ3})) as external prior weights and add a small positive number $\varepsilon$ to avoid zero denominator. Noted that $\mathbf{D}_{e}=\emptyset$ if $r=3p^{2}$ and $\mathbf{D}_{e}=\mathbf{U}_{k}$ if $r=0$. The dictionary $\mathbf{D} = [\mathbf{D}_{e}\ \mathbf{D}_{i}]$ is orthogonal by checking that:
\vspace{-2mm}
\begin{equation}\label{equ7}\vspace{-1mm}
\mathbf{D}^{T}\mathbf{D} = 
\left[\begin{array}{c}
\mathbf{D}_{e}^{T}
\\
\mathbf{D}_{i}^{T}
\end{array}\right]
[\mathbf{D}_{e}\ \mathbf{D}_{i}]
=
\left[\begin{array}{cc}
\mathbf{D}_{e}^{T}\mathbf{D}_{e}\ \mathbf{D}_{e}^{T}\mathbf{D}_{i}
\\
\mathbf{D}_{i}^{T}\mathbf{D}_{e}\ \mathbf{D}_{i}^{T}\mathbf{D}_{i}
\end{array}\right]
=
\mathbf{I}
\end{equation}

Similar to K-SVD \cite{ksvd}, we employ an alternating iterative framework to solve the optimization problem (\ref{equ5}). Specifically, we initialize the orthogonal dictionary as $\mathbf{D}_{(0)}=\mathbf{U}_{k}$ and for $t=0, 1, ..., T-1$, alternatively do:
\\
\textbf{Updating Sparse Coefficients}: given the orthogonal dictioanry $\textbf{D}_{(t)}$, we update the sparse coefficients via solving
\vspace{-2mm}
\begin{equation}\label{equ8}\vspace{-2mm}
\begin{split}
&\bm{\alpha}_{n}^{(t)}:=\argmin_{\bm{\alpha}_{n}\in\mathbb{R}^{3p^2\times 1}}
\|\mathbf{y}_{m}-\mathbf{D}_{(t)}\bm{\alpha}_{n}\|_{2}^{2}+\sum_{j=1}^{3p^{2}}\lambda_{j}|\bm{\alpha}_{n,j}|
\\
&
\text{s.t.}
\quad
\mathbf{D}_{(t)}=[\mathbf{D}_{e}\ \mathbf{D}_{i}],\ \mathbf{D}_{i}^{T}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{T}\mathbf{D}_{i} = \mathbf{0},
\end{split}
\end{equation}
Since dictionary $\mathbf{D}_{(t)}=[\mathbf{D}_{e}\ \mathbf{D}_{i}^{(t)}]$ is orthogonal, the problems (\ref{equ8}) has a closed-form solution \cite{pgpd} 
\vspace{-2mm}
\begin{equation}\label{equ9}\vspace{-2mm}
\hat{\bm{\alpha}}_{n}= \text{sgn}(\mathbf{D}_{(t)}^{T}\mathbf{y}_{n})\odot \text{max}(|\mathbf{D}_{(t)}^{T}\mathbf{y}_{n}|-\mathbf{\Lambda},\mathbf{0}),
\end{equation}
where $\mathbf{\Lambda} = [\lambda_{1},\lambda_{2},...,\lambda_{3p^2}]$ is the vector of regularization parameter and $\text{sgn}(\bullet)$ is the sign function, $\odot$ means element-wise multiplication.
\\
\textbf{Updating Orthogonal Dictionary}: given the sparse coefficients $\textbf{A}^{(t)}=[\bm{\alpha}_{1}^{(t)},...,\bm{\alpha}_{N}^{(t)}]$, we update the internal orthogonal dictionary via solving
\vspace{-2mm}
\begin{equation}\label{equ10} \vspace{-2mm}
\begin{split}
\textbf{D}_{i}^{(t+1)}
:
&
=
\argmin_{\textbf{D}_{i}}
\sum_{n=1}^{N}(\|\mathbf{y}_{n}-\mathbf{D}\bm{\alpha}_{n}^{(t)}\|_{2}^{2})
\\
&
=
\argmin_{\textbf{D}_{i}}
\|\mathbf{Y}-\mathbf{D}\mathbf{A}^{(t)}\|_{F}^{2}
\\
\text{s.t.}
\quad
\mathbf{D}
&
=
[\mathbf{D}_{e}\ \mathbf{D}_{i}],\ \mathbf{D}_{i}^{T}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{T}\mathbf{D}_{i} = \mathbf{0},
\end{split}
\end{equation}
Here we ignore the index $t$ for notation simplicity. The sparse coefficient matrix $\mathbf{A}=[\mathbf{A}_{e}^{T}\ \mathbf{A}_{i}^{T}]^{T}$ also has two parts: the external part $\mathbf{A}_{e}$ and the internal part $\mathbf{A}_{i}$ denote the coefficients over external dictionary $\mathbf{D}_{e}$ and internal dictionary $\mathbf{D}_{i}$, respectively. According to the Proposition 2.2 in \cite{bao2013fast}, the problem (\ref{equ9}) 
has a closed-form solution $\mathbf{D}_{i}^{*}=\mathbf{U}_{i}\mathbf{V}_{i}^{T}$, where $\mathbf{U}_{i}$ and $\mathbf{V}_{i}$ are the orthogonal matrices obtained by the following SVD
\vspace{-2mm}
\begin{equation}\label{equ11}\vspace{-2mm}
(\mathbf{I}-\mathbf{D}_{e}\mathbf{D}_{e}^{T})\mathbf{Y}\mathbf{A}_{i}^{T}
=
\mathbf{U}_{i}\mathbf{S}_{i}\mathbf{V}_{i}^{T}
\end{equation}

@@

\section{The Denoising Algorithm}

In this work, we solve the real noisy image denoising problem by employing the sparse coding framework \cite{pgpd} in Equ. (\ref{equ6}). We utilize two strategies to gain better performance: one is the 'Summed Area Table' \cite{sat} for faster patch group (PG) searching and the other is that the prior weights in Equ. (\ref{equ3}) are used for better denoising effects.

\subsection{Fast Internal Patch Group Searching}

Given a RGB image of size $256\times256\times3$, we can extract over 60 thousands local patches of size $6\times6\times3$. It is time-consumming to search patch groups (PG) for local patches one by one. To speed up the searching process, we employ the technique of 'Summed Area Table' \cite{sat} for efficient PG searching. The SAT permits to evaluate the sum of pixel values in rectangular regions of the image with four operations, regardless of the region size. Hence, we do not need do distance measure for each local patch.

\subsection{The Overall Algorithm}

With the solution $\hat{\boldsymbol{\upalpha}}$ in (\ref{equ13}), each column of the PG $\mathbf{Y}$ can be estimated as $\hat{\mathbf{y}}=\mathbf{D}\hat{\boldsymbol{\upalpha}}$. Then we add back its PG mean denoted as $\boldsymbol{\upmu}_{y}$ and reconstruct the clean image $\hat{\mathbf{x}}$ by aggregating all the estimated PGs. Similar to \cite{pgpd}, we perform the above denoising procedures for several iterations for better denoising outputs. But different from \cite{pgpd}, we do not employ the iterative regularization strategy \cite{osher2005iterative} since it is not effective in our method. The proposed denoising algorithm is summarized in Algorithm 1.
\begin{table}
\label{alg1}
\begin{tabular}{l}
\hline
\textbf{Alg. 1}: External PG Prior Guided Internal PG Prior
\\
\quad \quad \quad Learning for Real Image Denoising
\\
\hline
\textbf{Input:} Noisy image $\mathbf{y}$, external prior GMM model
\\
\textbf{Output:} The denoised image $\hat{\mathbf{x}}$.
\\
\textbf{Initialization:} $\hat{\mathbf{x}}^{(0)}=\mathbf{y}$;
\\
\textbf{for} $t = 1:IteNum$ \textbf{do}
\\
\quad\textbf{for} each PG $\mathbf{Y}_{n}$ \textbf{do}
\\
2.\quad Calculate group mean $\boldsymbol{\upmu}_{n}$ and form PG $\mathbf{\overline{Y}}_{n}$;
\\
3.\quad Gaussian component selection via Equ. (\ref{equ5});
\\
\quad\textbf{end for}
\\
\quad\textbf{for} each Internal Subspace \textbf{do}
\\
4.\quad Internal Subspace Learning by (\ref{equ4});
\\
5.\quad Recover each patch in all PGs via $\hat{\mathbf{x}}_{m}=\mathbf{D}\hat{\boldsymbol{\upalpha}}+\boldsymbol{\upmu}_{y}$;
\\
\quad\textbf{end for}
\\
6. Aggregate the recovered PGs of all subspaces to form
\\
\quad the recovered image $\hat{\mathbf{x}}^{(t)}$;
\\
\textbf{end for}
\\
\hline
\end{tabular}
\end{table}

@@

\begin{figure*}\label{fig2}
\centering
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (a) Noisy Image \\ (36.15dB/0.9523)    }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (h) Offline \\ (37.12dB/0.9776) }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (i) Online \\ (35.70dB/0.9755)  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (j) Guided \\ (\textbf{37.94}dB/\textbf{0.9804})}
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (h) Mean Image }
\end{minipage}
}
\caption{Denoised images of the image "Canon EOS 5D Mark3 ISO 3200 C1" by different methods. The images are better to be zoomed in on screen.}
\end{figure*}

>>>>

The rest of this paper will be summerized as follows: in Section 2, we briefly introduce the related work; in Section 3, we develop the proposed external prior guided internal prior learning model and formulate the overall image denoising algorithm; in Section 3, we demonstrate extensive experiments on real image denoising probelm; in Section 4, we conclude our paper and give future work.

\section{Related Work}

\subsection{Patch Group Prior of Natural Images}

@@

\section{External Patch Group Prior Guided Internal Prior Learning for Image Denoising}

\begin{figure*}\label{fig3}
\centering
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (a) Noisy Image \\ (36.15dB/0.9523)    }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (h) Offline \\ (37.12dB/0.9776) }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (i) Online \\ (35.70dB/0.9755)  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (j) Guided \\ (\textbf{37.94}dB/\textbf{0.9804})}
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (h) Mean Image }
\end{minipage}
}
\caption{Denoised images of the image "Canon EOS 5D Mark3 ISO 3200 C1" by different methods. The images are better to be zoomed in on screen.}
\end{figure*}

In this section, we formulate the framework of external patch group (PG) prior guided internal prior learning. We first introduce the external PG prior leaning on natural clean RGB images. Then we propose to employ the learned external PG prior to guide the internal prior (subspace selection and dictionary learning (DL)) learning of given degraded (such as noisy) images. Under the weighted sparse coding framework, the internal prior learning process has alternative closed-form solutions in term of updating sparse coefficients and orthogonal dictionary. Finally, we discuss in details how external prior learned from natural clean images guide the internal prior learning of given degraded (noisy) images.

@@

Now, we have clustered the PGs extracted from external clean images into $K$ Gaussians or subspaces. To better characterize each subspace, we perform singular value decomposition (SVD) on the covariance matrix:
\vspace{-2mm}
\begin{equation}\label{equ3}\vspace{-2mm}
\mathbf{\Sigma}_{k}=\mathbf{U}_{k}\mathbf{S}_{k}\mathbf{U}_{k}^{\top}.
\end{equation}
The singular vector matrices $\{\mathbf{U}_{k}\}_{k=1}^{K}$ are employed as the external orthogonal dictionary to guide the internal dictionary learning. The singular values in the diagonal of $\mathbf{S}_{k}$ reflect the significance of the singular vectors in $\mathbf{U}_{k}$ and utilized as prior weights for weighted sparse coding which will be discussed in next section.

@@

Given a real noisy image, assume we can totally extract $N$ local patches from it. Similar to the external prior learning stage, for the $n$-th local patch ($n=1,...,N$), we extract its similar patches around it to form a noisy PG denoted by $\mathbf{Y}_{n} = \{\mathbf{y}_{n,1},...,\mathbf{y}_{n,M}\}$. Then the group mean of $\mathbf{Y}_{n}$, denoted by $\bm{\mu}_{n}$, is calculated and subtracted from each patch, leading to the mean subtracted PG $\mathbf{\overline{Y}}_{n}$. Each mean substracted PG is defined as $\mathbf{\overline{Y}}_{n}\triangleq \{\mathbf{\overline{y}}_{n,m}\}_{m=1}^{M}$ where $\mathbf{\overline{y}}_{n,m}=\mathbf{y}_{n,m}-\bm{\mu}_{n}$. For adaptivity, we project the PG $\mathbf{\overline{Y}}_{n}$ into its most suitable Gaussian component (subspace) of the GMM learned on external PGs. The subspace most suitable for $\mathbf{\overline{Y}}_{n}$ is selected by firstly calculating the posterior probability of "$\mathbf{\overline{Y}}_{n}$ belonging to the $k$th Gaussian component":
\vspace{-2mm}
\begin{equation}\label{equ4}\vspace{-1mm}
P(k|\mathbf{\overline{Y}}_{n})=\frac{\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{y}}_{n,m}|\mathbf{0},\mathbf{\Sigma}_{k})}{\sum_{l=1}^{K}\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{y}}_{n,m}|\mathbf{0},\mathbf{\Sigma}_{l})},
\end{equation}
and then choosing the component with the maximum A-posteriori (MAP) probability $\ln P(k|\mathbf{\overline{Y}}_{n})$.

@@

Assume we have assigned all internal noisy PGs $\{\mathbf{\overline{Y}}_{n}\}_{n=1}^{N}$ to their corresponding most suitable Gaussians or subspaces in $\{\mathcal{N}(\mathbf{0},\mathbf{\Sigma}_{k})\}_{k=1}^{K}$. Assume $\{\mathbf{\overline{Y}}_{k_{n}}\}_{n=1}^{N_{k}}$ are the noisy PGs assigned to the $k$-th subspace, such that $\sum_{k=1}^{K}N_{k}=N$ and $\sum_{k=1}^{K}\sum_{n=1}^{N_{k}}k_{n}=NM$, we have that $\mathbf{\overline{Y}}_{k_{n}}=[\mathbf{y}_{k_{n},1},...,\mathbf{y}_{k_{n},M}]$. We consider to utilize the external orthogonal dictionary $\mathbf{U}_{k}$ to guide the learning of an orthogonal dictionary $\mathbf{D}_{k}:=[\mathbf{D}_{k,e}\ \mathbf{D}_{k,i}]\in \mathbb{R}^{3p^2\times 3p^2}$. This dictionary has two parts: the external part $\mathbf{D}_{k,e}=\mathbf{U}_{k}(:,1:3p^2-r)\in\mathbb{R}^{3p^2\times (3p^2-r)}$ is directly obtained from the external dictionary in Equ. (\ref{equ3}), and the internal part $\mathbf{D}_{k,i}$ is consisted of dictionary atoms adaptively learned from the internal noisy PGs $\mathbf{Y}_{k}$. The learning and denoising are simultaneously performed under the proposed reweighted sparse coding framework as f(for notation simplicity, we ignore the subspace index $k$):
\vspace{-2mm}
\begin{equation}\label{equ5}\vspace{-2mm}
\begin{split}
&\min_{\mathbf{D}_{i},\{\bm{\alpha}_{n}\}}
\sum_{n=1}^{N}(\|\mathbf{y}_{n}-\mathbf{D}\bm{\alpha}_{n}\|_{2}^{2}+\sum_{j=1}^{3p^{2}}\lambda_{j}|\bm{\alpha}_{n,j}|)
\\
&
\text{s.t.}
\quad
\mathbf{D}=[\mathbf{D}_{e}\ \mathbf{D}_{i}],\ \mathbf{D}_{i}^{\top}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{\top}\mathbf{D}_{i} = \mathbf{0},
\end{split}
\end{equation}
where $\lambda_{j}$ is the $j$-th regularization parameter defined as
\vspace{-2mm}
\begin{equation}\label{equ6}\vspace{-2mm}
\lambda_{j} = \lambda/(\sqrt{\mathbf{S}_{j}}+\varepsilon).
\end{equation}
We employ square roots of the singular values in $\mathbf{S}$ (please refer Equ. (\ref{equ3})) as external prior weights and add a small positive number $\varepsilon$ to avoid zero denominator. Noted that $\mathbf{D}_{e}=\emptyset$ if $r=3p^{2}$ and $\mathbf{D}_{e}=\mathbf{U}_{k}$ if $r=0$. The dictionary $\mathbf{D} = [\mathbf{D}_{e}\ \mathbf{D}_{i}]$ is orthogonal by checking that:
\vspace{-2mm}
\begin{equation}\label{equ7}\vspace{-1mm}
\mathbf{D}^{\top}\mathbf{D} = 
\left[\begin{array}{c}
\mathbf{D}_{e}^{\top}
\\
\mathbf{D}_{i}^{\top}
\end{array}\right]
[\mathbf{D}_{e}\ \mathbf{D}_{i}]
=
\left[\begin{array}{cc}
\mathbf{D}_{e}^{\top}\mathbf{D}_{e}\ \mathbf{D}_{e}^{\top}\mathbf{D}_{i}
\\
\mathbf{D}_{i}^{\top}\mathbf{D}_{e}\ \mathbf{D}_{i}^{\top}\mathbf{D}_{i}
\end{array}\right]
=
\mathbf{I}
\end{equation}

Similar to K-SVD \cite{ksvd}, we employ an alternating iterative framework to solve the optimization problem (\ref{equ5}). Specifically, we initialize the orthogonal dictionary as $\mathbf{D}_{(0)}=\mathbf{U}_{k}$ and for $t=0, 1, ..., T-1$, alternatively do:
\\
\textbf{Updating Sparse Coefficients}: given the orthogonal dictioanry $\textbf{D}_{(t)}$, we update the sparse coefficients via solving
\vspace{-2mm}
\begin{equation}\label{equ8}\vspace{-2mm}
\begin{split}
&\bm{\alpha}_{n}^{(t)}:=\argmin_{\bm{\alpha}_{n}\in\mathbb{R}^{3p^2\times 1}}
\|\mathbf{y}_{n}-\mathbf{D}_{(t)}\bm{\alpha}_{n}\|_{2}^{2}+\sum_{j=1}^{3p^{2}}\lambda_{j}|\bm{\alpha}_{n,j}|
\\
&
\text{s.t.}
\quad
\mathbf{D}_{(t)}=[\mathbf{D}_{e}\ \mathbf{D}_{i}],\ \mathbf{D}_{i}^{\top}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{\top}\mathbf{D}_{i} = \mathbf{0},
\end{split}
\end{equation}
Since dictionary $\mathbf{D}_{(t)}=[\mathbf{D}_{e}\ \mathbf{D}_{i}^{(t)}]$ is orthogonal, the problems (\ref{equ8}) has a closed-form solution \cite{pgpd} 
\vspace{-2mm}
\begin{equation}\label{equ9}\vspace{-2mm}
\hat{\bm{\alpha}}_{n}^{(t)}= \text{sgn}(\mathbf{D}_{(t)}^{\top}\mathbf{y}_{n})\odot \text{max}(|\mathbf{D}_{(t)}^{\top}\mathbf{y}_{n}|-\mathbf{\Lambda},\mathbf{0}),
\end{equation}
where $\mathbf{\Lambda} = [\lambda_{1},\lambda_{2},...,\lambda_{3p^2}]$ is the vector of regularization parameter and $\text{sgn}(\bullet)$ is the sign function, $\odot$ means element-wise multiplication.
\\
\textbf{Updating Orthogonal Dictionary}: given the sparse coefficients $\textbf{A}^{(t)}=[\bm{\alpha}_{1}^{(t)},...,\bm{\alpha}_{N}^{(t)}]$, we update the internal orthogonal dictionary via solving
\vspace{-2mm}
\begin{equation}\label{equ10} \vspace{-2mm}
\begin{split}
\textbf{D}_{i}^{(t+1)}
:
&
=
\argmin_{\textbf{D}_{i}}
\sum_{n=1}^{N}(\|\mathbf{y}_{n}-\mathbf{D}\bm{\alpha}_{n}^{(t)}\|_{2}^{2})
\\
&
=
\argmin_{\textbf{D}_{i}}
\|\mathbf{Y}-\mathbf{D}\mathbf{A}^{(t)}\|_{F}^{2}
\\
\text{s.t.}
\quad
\mathbf{D}
&
=
[\mathbf{D}_{e}\ \mathbf{D}_{i}],\ \mathbf{D}_{i}^{\top}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{\top}\mathbf{D}_{i} = \mathbf{0},
\end{split}
\end{equation}
Here we ignore the index $t$ for notation simplicity. The sparse coefficient matrix $\mathbf{A}=[\mathbf{A}_{e}^{\top}\ \mathbf{A}_{i}^{\top}]^{\top}$ also has two parts: the external part $\mathbf{A}_{e}$ and the internal part $\mathbf{A}_{i}$ denote the coefficients over external dictionary $\mathbf{D}_{e}$ and internal dictionary $\mathbf{D}_{i}$, respectively. According to the Proposition 2.2 in \cite{bao2013fast}, the problem (\ref{equ9}) 
has a closed-form solution $\mathbf{D}_{i}^{*}=\mathbf{U}_{i}\mathbf{V}_{i}^{\top}$, where $\mathbf{U}_{i}$ and $\mathbf{V}_{i}$ are the orthogonal matrices obtained by the following SVD
\vspace{-1mm}
\begin{equation}\label{equ11}\vspace{-2mm}
(\mathbf{I}-\mathbf{D}_{e}\mathbf{D}_{e}^{\top})\mathbf{Y}\mathbf{A}_{i}^{\top}
=
\mathbf{U}_{i}\mathbf{S}_{i}\mathbf{V}_{i}^{\top}
\end{equation}

@@

\subsection{The Denoising Algorithm}

As discussed in previous section, the proposed framework employs the external prior learned from natural clean images to guide the internal prior learning for any given noisy image. The image denoising is simultaneously done with the learning process. In the denoising procedure, for each subspace (we ignore the indexes $k=1,...,K$ of subspaces for notation simplicity), the group mean vectors $\{\bm{\mu}_{n}\}_{n=1}^{N}$ of the internal noisy PGs $\{\mathbf{y}_{n}\}_{n=1}^{N}$ are saved for reconstruction. Until now, we obtain the solutions of sparse coefficients $\{\hat{\bm{\alpha}}_{n}^{T-1}\}$ in (\ref{equ9}) and the orthogonal dictionary $\mathbf{D}_{(T)} = [\mathbf{D}_{e}\ \mathbf{D}_{i}^{(T)}]$ in Equ. (\ref{equ10}). Then the latent clean PGs $\{\hat{\mathbf{y}}_{n}\}_{n=1}^{N}$ are recovered by $\hat{\mathbf{y}}_{n}=\mathbf{D}_{}^{}\hat{\boldsymbol{\upalpha}}$. We add back its PG mean denoted as $\boldsymbol{\upmu}_{y}$ and reconstruct the clean image $\hat{\mathbf{x}}$ by aggregating all the estimated PGs. Similar to \cite{pgpd}, we perform the above denoising procedures for several iterations for better denoising outputs. But different from \cite{pgpd}, we do not employ the iterative regularization strategy \cite{osher2005iterative} since it is not effective in our method. The proposed denoising algorithm is summarized in Alg. 1.
\begin{table}
\label{alg1}
\begin{tabular}{l}
\hline
\textbf{Alg. 1}: External PG Prior Guided Internal PG Prior
\\
\quad \quad \quad Learning for Real Image Denoising
\\
\hline
\textbf{Input:} Noisy image $\mathbf{y}$, external prior GMM model
\\
\textbf{Output:} The denoised image $\hat{\mathbf{x}}$.
\\
\textbf{Initialization:} $\hat{\mathbf{x}}^{(0)}=\mathbf{y}$;
\\
\textbf{for} $t = 1:IteNum$ \textbf{do}
\\
1. Extracting internal patch groups (PGs) from $\hat{\mathbf{x}}^{(0)}$;
\\
\quad\textbf{for} each PG $\mathbf{Y}_{n}$ \textbf{do}
\\
2.\quad Calculate group mean $\boldsymbol{\upmu}_{n}$ and form PG $\mathbf{\overline{Y}}_{n}$;
\\
3.\quad Gaussian component selection via Equ. (\ref{equ5});
\\
\quad\textbf{end for}
\\
\quad\textbf{for} each Internal Subspace \textbf{do}
\\
4.\quad Internal Subspace Learning by (\ref{equ4});
\\
5.\quad Recover each patch in all PGs via $\hat{\mathbf{x}}_{m}=\mathbf{D}\hat{\boldsymbol{\upalpha}}+\boldsymbol{\upmu}_{y}$;
\\
\quad\textbf{end for}
\\
6. Aggregate the recovered PGs of all subspaces to form
\\
\quad the recovered image $\hat{\mathbf{x}}^{(t)}$;
\\
\textbf{end for}
\\
\hline
\end{tabular}
\end{table}

@@

\begin{table*}\label{tab1}
\caption{Average PSNR(dB) results of different methods on 60 cropped real noisy images captured in \cite{crosschannel2016}.}
\label{tab1}
\begin{center}
\renewcommand\arraystretch{1}
\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|c|}
\hline
 & \textbf{Noisy} &\textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}&\textbf{TRD}& \textbf{NI}& \textbf{NC} &\textbf{Guided}  &\textbf{Guided2} 
\\
\hline
PSNR & 34.51 & 34.58 & 34.52 & 36.19 & 37.40 & 37.75 & 36.53 & 37.57 &  \color{blue}{38.72} & \color{red}{ 38.90}
\\
\hline
SSIM & 0.8718  & 0.8748  & 0.8743   & 0.9470 & 0.9598 &  0.9617 & 0.9241  &  0.9514  & \color{blue}{0.9694} & \color{red}{0.9702}
\\
\hline
\end{tabular}
\end{center}
\end{table*}
